Cover letter

### 2018-06-13 output/Paper.Rmd
finalised updates for vaccine

---
title: '**Title:** Exploring the effects of BCG vaccination in patients diagnosed with tuberculosis: observational study using the Enhanced Tuberculosis Surveillance system'
author: "Sam Abbott, Hannah Christensen, Maeve K Lalor, Dominik Zenner, Colin Campbell, Mary Ramsay, Ellen Brooks-Pollock"
csl: ../common/vaccines.csl
output:
  word_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 8
    reference_docx: ../common/style.docx
  html_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 8
  pdf_document: default
  html_notebook: null
bibliography: ../common/library.bib
---

@@

- Is there evidence in the Enhanced Tuberculosis (TB) Surveillance System that BCG vaccination improves TB outcomes?

- This analysis suggests that vaccination with BCG is associated with reduced all-cause mortality for TB patients and potentially a reduced chance of having a repeat episode.

@@

- BCG vaccination could reduce all-cause mortality in TB cases and may decrease the number of repeat episodes in low incidence countries.

>>>>

---
title: '**Title:** Exploring the effects of BCG vaccination in patients diagnosed with tuberculosis: observational study using the Enhanced Tuberculosis Surveillance system'
author: "Sam Abbott, Hannah Christensen, Maeve K Lalor, Dominik Zenner, Colin Campbell, Mary Ramsay, Ellen Brooks-Pollock"
csl: ../common/vaccine.csl
output:
  word_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 8
    reference_docx: ../common/style.docx
  html_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 8
  pdf_document: default
  html_notebook: null
bibliography: ../common/library.bib
---

@@

- Found evidence of an association between BCG vaccination and reduced all-cause mortality in TB cases.

- Weaker evidence of an association between BCG vaccination and reduced repeat TB episodes in TB cases.

@@

- We explored the identified associations by age and time since vaccination.

### 2018-06-13 output/cover_letter/cover_letter.Rmd
packrat updates, added new version DOI
finalised updates for vaccine

---
title: "Cover letter"
output:
    word_document: 
        reference_docx: ../../common/style.docx
    html_notebook: default
---

@@

We feel our manuscript will be of interest to you and the journal's readership because Bacillus Calmette-Guérin (BCG) is one of the most widely-used vaccines worldwide and our study explores possible additional benefits from vaccination. We found evidence to suggest that vaccination with BCG is associated with reduced all-cause mortality for TB patients and weaker evidence of an association with a reduced chance of having a repeat episode. Recognition of such benefits could lead to a re-evaluation of BCG policy, both in low and high incidence countries. Our study benefits from the use of data from the Enhanced Tuberculosis surveillance system, which contains data on demographics, microbiology and outcomes of active TB cases in England. We made use of logistic regression, with both complete case analysis and multiply imputed data, to explore the effects of BCG vaccination in this robust dataset.

>>>>

---
title: ""
output:
    word_document: 
        reference_docx: ../../common/style.docx
    html_notebook: default
---

@@

We feel our manuscript will be of interest to you and the journal's readership because Bacillus Calmette-Guérin (BCG) is one of the most widely-used vaccines worldwide and our study explores possible additional benefits from vaccination. We found evidence to suggest that vaccination with BCG is associated with reduced all-cause mortality for TB patients and weaker evidence of an association with a reduced chance of having a repeat episode. Recognition of such benefits could lead to a re-evaluation of BCG policy, both in low and high incidence countries. We investigated, but could not find conclusive evidence that, the association with reduced all-cause mortality was due to an association between BCG vaccination and reduced TB mortality. Our study benefits from the use of data from the Enhanced Tuberculosis surveillance system, which contains data on demographics, microbiology and outcomes of active TB cases in England. We made use of logistic regression, with both complete case analysis and multiply imputed data, to explore the effects of BCG vaccination in this robust dataset.
